Have you forgotten?' Conversion experiences in list worlds

### 2016-10-18 lists_conversion_experience.rmd
adding a bit on propensities

---
title: "An Example Using the Tufte Style"
author: "John Smith"
output:
  tufte::tufte_handout: default
tufte::tufte_html: default
---

@@

```{r setup, cache=FALSE, include=FALSE}
library(knitr)
output <- opts_knit$get("rmarkdown.pandoc.to")
opts_chunk$set(warnings=FALSE)
opts_chunk$set(messages=FALSE)
```

@@

Shopping lists are quite prosaic -- a dozen lines scrawled on the back of a used envelope stuck on the refrigerator door  -- and sublime -- a million products ranked in some kind of order for tens or hundreds of millions of people. I regard the list of five suggestions show to Tesco's online customers at the checkout as symptomatic of a major contemporary form of ordering, the recommendation list, that we see in many  forms of news, media, entertainment, marketing, advertising.

@@

```{r simulate_basket, echo=FALSE, cache=TRUE}
library(dplyr)
library(ggplot2)
library(readr)

@@

```{r arules, echo=TRUE}
library(arules)
library(arulesViz)
library(datasets)
data(Groceries)
itemFrequencyPlot(Groceries,topN=20,type="absolute")
# Get the rules
rules <- apriori(Groceries, parameter = list(supp = 0.001, conf = 0.8))

@@

```{r tesco, cache=TRUE, }
    library(ggplot2)
    tesco = read.csv('data/reference_data/tesco_groceries.csv')
    total = sum(tesco$actual, na.rm=TRUE) 
    tesco = na.omit(tesco)
    tesco$actual = as.integer(tesco$actual)

@@

Similarly, to model the potential complementarities   between things entails a matrix of comparisons. `Nutella` complements `bananas,` but the converse is not necessarily true since `bananas` need not complement `nutella.`  If then the

## 13. Complementarity drives conversion 
- the problem of action

>>>>

---
title: "'Have you forgotten?' Conversion experiences in list worlds"
author: "Adrian Mackenzie"
date: "`r Sys.Date()`"
output:
tufte::tufte_handout: default
citation_package: biber
latex_engine: xelatex
bibliography: ~/ref_bibs/uni.bib
link-citations: yes
---

@@

```{r setup, cache=FALSE, include=FALSE}
library(knitr)
library(tint)
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tint'))
options(htmltools.dir.version = FALSE)
output <- opts_knit$get("rmarkdown.pandoc.to")
opts_chunk$set(warning=FALSE)
opts_chunk$set(message=FALSE)
opts_chunk$set(error=TRUE)
```

@@

Shopping lists such as Figure \ref{fig:shopping_list} are quite prosaic -- a dozen lines scrawled on the back of a used envelope stuck on the refrigerator door  -- and sublime -- a million products ranked in some kind of order for tens or hundreds of millions of people. I regard the list of five suggestions show to Tesco's online customers at the checkout as symptomatic of a major contemporary form of ordering, the recommendation list, that we see in many  forms of news, media, entertainment, marketing, advertising.

@@

```{r simulate_basket, echo=FALSE, cache=TRUE, fig.margin=TRUE}
library(dplyr)
library(ggplot2)
library(readr)

@@

```{r arules, echo=TRUE, fig.margin=TRUE}
library(arules)
library(arulesViz)
library(datasets)
data(Groceries)
itemFrequencyPlot(Groceries,topN=20,type="absolute")
# Get the rules
rules <- apriori(Groceries, parameter = list(supp = 0.001, conf = 0.8))

@@

```{r tesco, cache=TRUE, fig.margin=TRUE}
    library(ggplot2)
    tesco = read.csv('data/reference_data/tesco_groceries.csv')
    total = sum(tesco$actual, na.rm=TRUE) 
    tesco = na.omit(tesco)
    tesco$actual = as.integer(tesco$actual)

@@

## 13. Complementarity drives conversion

![propensity_matrix](figure/propensity_conversions.png)

Similarly, to model the potential complementarities   between things entails a matrix of comparisons. `Nutella` complements `bananas,` but the converse is not necessarily true since `bananas` need not complement `nutella.`

How should we understand the effect of complementarity? Patel says that 'complementarity drives conversion.' That is, the matrix of similarities expressed as numerical associations between products best animates the conversion of recommendations into purchases.

In the similarity matrix, shaped by the history of past recommendations and purchases made by this customer, lie the propensities of things that Hansen (following Popper) attributes to the world. Karl Popper speaks of the future as a 'crystallization of propensities' [@Popper_1990,18]
